International Relations are a Social Network:\\ A Latent Network Approach for Global Politics

### 2017-10-21 paper/4_app.tex
more changes

% TO DO: include discussion and analysis of different K's in appendix (for M cD)
\begin{figure}
\includegraphics[width=\textwidth]{McDonald_coefs.pdf}
\caption{\label{fig:mcdCoefs}Coefficient plot of McDonald (2004)'s original model (blue) compared to AME model (red).}
\end{figure}
\FloatBarrier
%\begin{figure}
%\centering   
%\subfigure[AUC]{\label{fig:mcDauc}\includegraphics[width=65mm]{McDonald_auc_outsamp.pdf}}
%\subfigure[Precision and Recall]{\label{fig:mcDpr}\includegraphics[width=65mm]{McDonald_pr_outsamp.pdf}}
%\caption{\label{fig:mcdall} Assessments of out-of-sample predictive performance for McDonald (2004) using ROC curves and PR curves.}
%\end{figure}

Our re-estimation with AME reveals that trade relations are highly interdependent and exhibit important patterns of transitivity.  Or, in other words, if countries $i$ and $j$ are highly dependent and countries $j$ and $k$ are also highly dependent, then we are likely to observe high dependency between countries $i$ and $k$. Our findings support those of Traag and Lupu (2013) which argue that indirect trade relations reduce the probability of conflict. This indicates that conflict is less likely between members of a trade community. Once we control for these dependencies, we can more clearly interpret the positive link between trade and conflict. Figure~\ref{fig:mcdCoefs} shows the coefficients for both the original and AME model. The most striking thing is that AME finds a positive---not negative as found by McDonald---association between trade dependence and conflict. The AME coefficient is not only in the opposite direction, but it is approximately three times more precisely estimated.  At the same time, the AME has ROC and PR curves (not shown) that dominate the OLS results found in McDonald (2004).

>>>>

% TO DO: include discussion and analysis of different K's in appendix (for M cD)
%\begin{figure}
%%\includegraphics[width=\textwidth]{McDonald_coefs.pdf}
%\caption{\label{fig:mcdCoefs}Coefficient plot of McDonald (2004)'s original model (blue) compared to AME model (red).}
%\end{figure}
%\FloatBarrier
%\begin{figure}
%\centering   
%\subfigure[AUC]{\label{fig:mcDauc}\includegraphics[width=65mm]{McDonald_auc_outsamp.pdf}}
%\subfigure[Precision and Recall]{\label{fig:mcDpr}\includegraphics[width=65mm]{McDonald_pr_outsamp.pdf}}
%\caption{\label{fig:mcdall} Assessments of out-of-sample predictive performance for McDonald (2004) using ROC curves and PR curves.}
%\end{figure}

Our re-estimation with AME reveals that trade relations are highly interdependent and exhibit important patterns of transitivity.  Or, in other words, if countries $i$ and $j$ are highly dependent and countries $j$ and $k$ are also highly dependent, then we are likely to observe high dependency between countries $i$ and $k$. Our findings support those of Traag and Lupu (2013) which argue that indirect trade relations reduce the probability of conflict. This indicates that conflict is less likely between members of a trade community. Once we control for these dependencies, we can more clearly interpret the positive link between trade and conflict.  The most striking thing is that AME finds a positive conditional association between trade dependence and conflict ($\hat{\beta}= 18.4, \quad \sigma_{\hat{\beta}} = 28.6$), while the comparable numbers for the logistic regression found in the original articles are negative ($\hat{\beta}= -22.2, \quad \sigma_{\hat{\beta}} = 15.2$). 
%The AME coefficient is not only in the opposite direction, but it is approximately three times more precisely estimated.  
At the same time, the AME has ROC and PR curves (shown in the Appendix) that dominate the results found in McDonald (2004).
